On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-06-25 docs/mvfits_paper/mvf.tex
adding Yang:2012pj ref near mention of asymptotic degeneracy

We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015trm}.

>>>>

We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Yang:2012pj,Zimmerman:2015trm}.
